---
title: "Joseph Outa, Reproducibility Report: Group B Choice 3"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

-------

For this exercise, please try to reproduce the results from Experiment 2 of the associated paper (de la Fuente, Santiago, Roman, Dumitrache, & Casasanto, 2014). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary: 

Researchers tested the question of whether temporal focus differs between Moroccan and Spanish cultures, hypothesizing that Moroccans are more past-focused, whereas Spaniards are more future-focused. Two groups of participants ($N = 40$ Moroccan and $N=40$ Spanish) completed a temporal-focus questionnaire that contained questions about past-focused ("PAST") and future-focused ("FUTURE") topics. In response to each question, participants provided a rating on a 5-point Likert scale on which lower scores indicated less agreement and higher scores indicated greater agreement. The authors then performed a mixed-design ANOVA with agreement score as the dependent variable, group (Moroccan or Spanish, between-subjects) as the fixed-effects factor, and temporal focus (past or future, within-subjects) as the random effects factor. In addition, the authors performed unpaired two-sample t-tests to determine whether there was a significant difference between the two groups in agreement scores for PAST questions, and whether there was a significant difference in scores for FUTURE questions.

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 2):

> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjectS factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2). Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001. (de la Fuente et al., 2014, p. 1685).

------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files

# #optional packages/functions:
# library(afex) # anova functions
# library(ez) # anova functions 2
# library(scales) # for plotting
# std.err <- function(x) sd(x)/sqrt(length(x)) # standard error
```

# Step 2: Load data

```{r}
# Just Experiment 2
data_path <- 'data/DeLaFuenteEtAl_2014_RawData.xls'
d <- read_excel(data_path, sheet=3)
```

# Step 3: Tidy data

```{r}
head(d)
length(d)
filterd_d <- select(d, -item) 
colnames(filterd_d)
names(filterd_d)[4] <- "Agreement"

#summarize 
sorted_d <- filterd_d %>%
group_by(participant, group, subscale)%>%
  summarise(Agreement=mean(Agreement))
sorted_d
length(sorted_d$participant) #check data frame length

#make data wide
tpf_long <- sorted_d  %>%
  pivot_wider(names_from = "subscale",
              values_from = "Agreement")

#check sample size
length(tpf_long$participant) #equals 80 that's good

#re-sort by condition
tpf_long_2 <- arrange(tpf_long, group)
names(tpf_long_2)[2] <- "Country"
names(tpf_long_2)[3] <- "Future"
names(tpf_long_2)[4] <- "Past"

tpf_long_2

```

# Step 4: Run analysis

## Pre-processing

```{r}
#compute summary stats
tpf_summ <- tpf_long_2 %>%
  group_by(Country) %>%
  summarise(FutureMean = mean(Future), PastMean = mean(Past))
tpf_summ 

```

## Descriptive statistics

Try to recreate Figure 2 (fig2.png, also included in the same folder as this Rmd file):

```{r}

```

## Inferential statistics

> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjects factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2).

```{r}
# reproduce the above results here

```

> Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, 

```{r}
# reproduce the above results here

```

> and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001.(de la Fuente et al., 2014, p. 1685)

```{r}
# reproduce the above results here

```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> No, was unable to complete it in 3 hours It was a steep learning curve to figure out the code for tidying the data. I could have kept going but it would take me longer than I have time for. I got stuck at the pre-processing stage. I couldn't generate a table with summary statistics. I think its because I couldn't group the table with the 'participant' column still there and I couldn't figure out a way around it. 
 
How difficult was it to reproduce your results? 

> I think the hardest part is the data wrangling.

What aspects made it difficult? What aspects made it easy?

> Since I am a beginner I had to look up things quite a lot and it took a lot of time. I am also often not sure if I'm doing the right thing. I definitely need to practice this more when I have more time. 
